A new model to predict survival in patients with end-stage liver disease

### 2022-07-22 analysis/supplement.Rmd
refactor: apply proofreading suggestions

# Benchmark results of machine learning algorithms

```{r benchmark-plot, fig.cap = "Benchmark results of machine learning algorithms.", echo = FALSE, fig.width = 18, fig.height = 12}
tar_load(bmrk_results)
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r benchmark-table, echo = FALSE}
agg <- bmrk_results$aggregate(msr("surv.cindex", id = "harrell"))
agg[, `:=`
    (nr = NULL, resample_result = NULL, resampling_id = NULL, iters = NULL)
]
agg <- subset(agg, task_id == "zlog_eldd" & !grepl("^scale", learner_id))
agg[, task_id := NULL]
setorder(agg, -harrell)
knitr::kable(
    agg,
    col.names = c("Learner ID", "Harrell C"),
    caption = paste0("Benchmark results. Ranking of the ", nrow(agg), " tested machine learning algorithms.")
)
```

@@

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, fig.cap = "Trend in AUROC. Trend in the area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na and MELD-Plus7 as described in [@blanche2013]."}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)

>>>>

# Benchmark results of machine-learning algorithms

```{r benchmark-plot, fig.cap = "Benchmark results of machine-learning algorithms.", echo = FALSE, fig.width = 18, fig.height = 12}
tar_load(bmrk_results)
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r benchmark-table, echo = FALSE}
agg <- bmrk_results$aggregate(msr("surv.cindex", id = "harrell"))
agg[, `:=`
    (nr = NULL, resample_result = NULL, resampling_id = NULL, iters = NULL)
]
agg <- subset(agg, task_id == "zlog_eldd" & !grepl("^scale", learner_id))
agg[, task_id := NULL]
setorder(agg, -harrell)
knitr::kable(
    agg,
    col.names = c("Learner ID", "Harrell C"),
    caption = paste0("Benchmark results. Ranking of the ", nrow(agg), " tested machine-learning algorithms.")
)
```

@@

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, fig.cap = "Trend in the area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, and MELD-Plus7, as described in [@blanche2013]."}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)
